### 2013-03-28 doc/sosp13/evaluation.tex
overall paragraph cleanup
histogram characterization

Figure~\ref{fig:grappa-comparisons} shows the results. Overall, \Grappa is
within striking distance of XMT and UPC performance. However, it underperforms
compared to hand-tuned MPI. Nevertheless, this comparison needs to be taken
with a grain of salt for several reasons. First, we have not spent as much
time tuning \Grappa's implementations. This is supported by inspecting the BFS
MPI implementation we used, which clearly shows that it employs a lot of
algorithmic-specific optimizations. In fact, some of these optimizations
resemble some of what \Grappa does automatically, like message aggregation.
Second, the GUPS results presented earlier suggests that \Grappa performance
can do a lot better. \TODO{update this once we have more results. }

@@

In UTS, we obtained the best throughput by flushing frequently: on the order 100 microseconds , but
this mean

In BFS, we see a trimodal distribution. There are two reasons for
this. First, in BFS, we obtained the best throughput by flushing at
least 500 microseconds apart, but also flushing whenever the core went
idle. This leads to a large number of messages that are not

@@

The bimodal nature of the BFS distribution is due to a locality optimization that o

Both

In BFS we exploit a large
 Since we are traversing power-law graphs,
some vertices have a very high number of edges. We exploit locality in
BFS by having tasks visit vertices whose edge lists are stored on the
local node. When this local traversal hits a high-degree vertex, BFS
is able to generate a large number of

Figure \ref{fig:grappa-latency} shows

We see different aggregation behavior between BFS and UTS:

In BFS, the bulk of remote accesses are done to take owner

Conversely, UTS attempts to

Distribution if possible. With and without aggregation.

@@

\paragraph{Work stealing behavior.}
Performance loss of not having stealing. Ratio of \# of steals over total \# of task spawns. UTS needs stealing to work.

>>>>

Figure~\ref{fig:grappa-comparisons} shows the results. Overall, \Grappa is
within striking distance of XMT and well beyond UPC performance (UTS only).
However, it underperforms compared to hand-tuned MPI. Nevertheless, this
comparison needs to be taken with a grain of salt for several reasons. First,
we have not spent as much time tuning \Grappa's implementations. This is
supported by inspecting the BFS MPI implementation we used, which clearly
shows that it employs a lot of algorithmic-specific optimizations. In fact,
some of these optimizations resemble some of what \Grappa does automatically,
like message aggregation. Second, the GUPS results presented earlier suggests
that \Grappa performance can do a lot better. 
% \TODO{update this once we have more results. }

@@

@@

In UTS, we obtained the best throughput by flushing frequently: on the
order 100 microseconds. This, combined with the fewer number of remote
accesses, means that there are a limited nubmer of requests generated
per flush interval, leading to packets primarily smaller than 10KB.

In BFS, we see a trimodal distribution. There are two reasons for
this. First, in BFS, we obtained the best throughput by flushing at
least 500 microseconds apart, and also flushing whenever the core went
idle. Since this process ignores whether another flush has occured
recently, it leads to a large number of small messages. This leads to
the first and smallest mode of the distribution.

The other two modes are due to a locality optimization in the \Grappa
version of BFS. To minimize unnecessary remote communication, each
core visits vertices whoes edge lists are stored locally. Since we are
traversing power-law graphs, a small fraction of vertices have a very
high number of edges. This means that occasionally a core visits a
high-degree vertex which allows it to very quickly generate a large
batch of requests. This interacts well with aggregation; when we find
high degree vertices, we are able to aggregate packets on the order of
40KB. In flush intervals without high-degree vertices, we see packets
on the order of 8KB.

Figure \ref{fig:grappa-latency} shows the latency distribution of
remote delegate operations. This distribution follows the aggregated
message size distribution: when we form larger packets, the system
takes longer to process them.

@@
